Windowed Developer Topic Analysis

### 2009-04-09 lda-paper.tex
Some latest edits

The third most common trend, seen on Figure \ref{fig:trend}, seemed to
include tokens related to operating system support, such as Linux and
Windows, as well as architecture support, AMD64 and Opteron. The word
problem was common among all of those trends. This trend seemed
related to the smaller fourth largest trend which occurred nearby it
that had AMD64 and Windows tokens.

>>>>

The third most common trend, seen on Figure \ref{fig:trendtimeline}, seemed to
include tokens related to operating system support, such as Linux and
Windows, as well as architecture support, AMD64 and Opteron. The word
problem was common among all of those trends. This trend seemed
related to the smaller fourth largest trend which occurred nearby it
that had AMD64 and Windows tokens.
